Supplementary Information

### 2020-07-30 doc/manuscript/MEE_manuscript.Rmd
add new DBH figure

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; Front Royal, VA 22630, USA
2. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama
X#. Harvard Forest, Petersham, MA 01366, USA
X#. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada

@@

![**Figure 4 | Growth sensitivity to DBH:** (a) $\Delta r$, (b) $BAI$, (c) $\Delta AGB$. THIS FIGURE IS JUST A ROUGH COMPILATION OF RESULTS SO FAR (including known issues--e.g., SCBI). Ideally, I'd like to plot all sites together, meaning we probably have to lose species IDs (plots with species IDs can be shown in appendix).](tables_figures/size_figure_sketch.png)

>>>>

1. Conservation Ecology Center; Smithsonian Conservation Biology Institute; Front Royal, VA 22630, USA

2. Center for Tropical Forest Science-Forest Global Earth Observatory; Smithsonian Tropical Research Institute; Panama, Republic of Panama

X#. Harvard Forest, Petersham, MA 01366, USA

X#. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada

@@

![**Figure 4 | Growth sensitivity to DBH: (a) $\Delta r$, (b) $BAI$, (c) $\Delta AGB$.** It's tough to fit all the plots, so we may have to adjust this somehow.](tables_figures/DBH_responses.png)
